### 2020-02-12 writeup/setup.tex
edit

\section{Problem setup}

\begin{enumerate}
%    \item {\bf The distributed learning problem.}
%    \begin{align}
 %     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
 %   \end{align}
 %   A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spetrum.
 %   This is also known as covariate shift in the literature.
 %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
  \item {\bf The multi-task learning problem.} \\
    {\it Different covariates:}
    If we follow the model setup of the first problem, but consider the following objective instead.
    \begin{align}
        f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
    \end{align}
    This is a slightly more complicated parameterization of the first problem, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

    {\it Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
    Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
\end{enumerate}

>>>>

\section{Problem setup: The multi-task learning problem}\label{sec_setup}

%    \item {\bf The distributed learning problem.}
%    \begin{align}
 %     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
 %   \end{align}
 %   A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spetrum.
 %   This is also known as covariate shift in the literature.
 %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.

    \paragraph{Different covariates:}
    If we follow the model setup of the first problem, but consider the following objective instead.
    \begin{align}
        f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
    \end{align}
    This is a slightly more complicated parameterization of the first problem, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

    \paragraph{Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
    Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
